Periodograms for Multiband Astronomical Time Series

### 2017-01-05 writeup/paper.tex
Typo: \pre->pre

As an example of one of these generalizations, we'll consider 
what has variously been called the {\it Date-compensated Discrete Fourier Transform} \citep{Ferraz-Mello81}, the {\it floating-mean periodogram} \citep{Cumming99}, and the {\it generalized Lomb-Scargle method} \citep{Zechmeister09}. Here we use the term {\it floating-mean periodogram}. This method adjusts the classic normalized periodogram by fitting the mean of the model alongside the amplitudes:
\begin{equation}
  y(t~|~\omega, \theta) = \theta_0 + \theta_1\sin\omega t + \theta_2\cos\omega t
\end{equation}
The periodogram derived from this model can be more accurate than the standard \pre-centered periodogram for certain observing cadences and selection functions, and espeically when searching for long-period varaibility or working with very few samples \citep{Cumming99}. \citet{Zechmeister09} detail the required modifications to the orthogonalized harmonic formalism of \eq{LombScargle} to allow the mean to float in the model. In the matrix formalism, the modification is much more straightforward: all that is required is to add a column of ones to the $X_\omega$ matrix before computing the power via \eq{LombScargle2}. This column of ones corresponds to a third entry in the parameter vector $\theta$, and acts as a uniform constant offset for all data points.

>>>>

As an example of one of these generalizations, we'll consider 
what has variously been called the {\it Date-compensated Discrete Fourier Transform} \citep{Ferraz-Mello81}, the {\it floating-mean periodogram} \citep{Cumming99}, and the {\it generalized Lomb-Scargle method} \citep{Zechmeister09}. Here we use the term {\it floating-mean periodogram}. This method adjusts the classic normalized periodogram by fitting the mean of the model alongside the amplitudes:
\begin{equation}
  y(t~|~\omega, \theta) = \theta_0 + \theta_1\sin\omega t + \theta_2\cos\omega t
\end{equation}
The periodogram derived from this model can be more accurate than the standard pre-centered periodogram for certain observing cadences and selection functions, and espeically when searching for long-period varaibility or working with very few samples \citep{Cumming99}. \citet{Zechmeister09} detail the required modifications to the orthogonalized harmonic formalism of \eq{LombScargle} to allow the mean to float in the model. In the matrix formalism, the modification is much more straightforward: all that is required is to add a column of ones to the $X_\omega$ matrix before computing the power via \eq{LombScargle2}. This column of ones corresponds to a third entry in the parameter vector $\theta$, and acts as a uniform constant offset for all data points.
